Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-07 paper/sections/acknowledgements.tex
[ paper ] appendix added.
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

*

% -*- root: main.tex -*-
\documentclass[main.tex]{subfiles}
\begin{document}

@@

We thank Joe Leslie-Hurd for his support with \Metis prover. We also
acknowledge the work carried out by Alejandro G\'omez-Londo\~no~
\cite{Gomez-Londono2015} used as the basis code for our \TSTP
parsing module.
\improvement{We should consider thank Kanso and Anton, to provide us
their thesis, discussion, and source code to compare with our work?}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}

@@

We thank Joe Leslie-Hurd for his support with \Metis prover. We also
acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
parsing module.
% \improvement{We should consider thank Kanso and Anton, to provide
% us their thesis, discussion, and source code to compare with our
% work?}

### 2017-10-07 paper/sections/metis-language-and-proofs.tex
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ paper ] minor changes.

\textit{Splitting}. To prove a goal, \Metis splits the goal into
disjoint cases. This process produces a list of new subgoals, the
conjunction of these subgoals implies the goal. Then, a proof of the
goal becomes in smaller proofs, one refutation for each subgoal.
These subgoals are introduced in the \TSTP derivation with the \strip
inference rule. We refer the reader to see Theorem~\ref{thm:thm-strip}.

@@

\textit{Clausification.} The \clausify rule transforms a
propositional formula in clausal normal form, a conjunction
of clauses. Where a \emph{clause} is the disjunction of zero or more
literals and a \emph{literal} is an atom (positive literal) or a
negation of an atom (negative literal). Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation. We refer the reader to see Theorem~\ref{thm:thm-clausify}.

@@

\textit{Resolution.} The \resolve rule is the resolution theorem
showed in Fig.~\ref{fig:metis-inferences}. For its application, we
need the positive literal for resolution and two derivations to
deduce the \emph{resolvent}. The positive literal $p$ must occur in
the formula from the first derivation, and the negative literal must
occur in the formula from the second derivation (this follows the
same pattern in \Metis' logic core in Fig.~\ref{fig:metis-inferences}
for the resolve inference).
We refer the reader to see Theorem~\ref{thm:thm-resolve}.

@@

\textit{Splitting a conjunct.} The \conjunct rule extracts from a
conjunction one of its conjuncts; it is a generalization of the
projection rules for the conjunction connective as the
following \TSTP derivation shows.
We refer the reader to see Theorem~\ref{thm:thm-conjunct}.

>>>>

\textit{Splitting}. To prove a goal, \Metis splits the goal into
disjoint cases. This process produces a list of new subgoals, the
conjunction of these subgoals implies the goal. Then, a proof of the
goal becomes in smaller proofs, one refutation for each subgoal.
These subgoals are introduced in the \TSTP derivation with the \strip
inference rule. We refer the reader to see Section~\ref{sssec:splitting-goal} for the formalization of \strip rule.

@@

\textit{Clausification.} The \clausify rule transforms a
propositional formula in clausal normal form, a conjunction
of clauses. Where a \emph{clause} is the disjunction of zero or more
literals and a \emph{literal} is an atom (positive literal) or a
negation of an atom (negative literal). Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation. We refer the reader to see Section~\ref{sssec:clausification} for the formalization of \clausify rule.

@@

% ...................................................................
\vskip 2mm

\textit{Resolution.} The \resolve rule incorporates  the resolution theorem showed in Fig.~\ref{fig:metis-inferences} with
three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.

The positive literal $l$ must occur in
the formula from the first derivation $\mathcal{D}₁$, and the
negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in \Metis' logic core for the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}).
We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.

@@

\textit{Splitting a conjunct.} The \conjunct rule extracts from a
conjunction one of its conjuncts; it is a generalization of the
projection rules for the conjunction connective as the
following \TSTP derivation shows.
We refer the reader to see Theorem~\ref{thm:thm-conjunct}
in Section~\ref{sssec:splitting-a-conjunct} for its formalization.
